### 2018-08-07 paper/design.tex
added caption for overview figure

% Figure~\ref{fig:outline} shows the components needed to obtain the
% routing information for the headers.

% \begin{figure}[t]
%   \centering
%   \def\svgwidth{0.8\columnwidth}
%   \import{figures/}{outline_figure_only.pdf_tex}
%   \caption{\label{fig:outline}%
%     %\commentDaniel{We must adapt this figure to the text.}%
%     Outline of \name's components. Users' squads of devices are circled in gray. 
%     From top to bottom: a user's devices collaborate through the Squad Overlay 
%     (\cref{sec:squad_overlay}); online devices globally share information about 
%     them with random peers (\cref{ssec:device_availability}); using the two 
%     overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
%     These protocols enable secure file transfer between users 
%     (\cref{ssec:por}).}
% \end{figure}

>>>>

%% Figure~\ref{fig:outline} shows the components needed to obtain the
%% routing information for the headers.

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  %  \import{figures/}{outline_figure_only.pdf_tex}
    \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
    \caption{Architectural overview of the \ac{SPORES} private file sharing service. \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploit decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.}
    \label{fig:outline}
\end{figure}
